First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-07-11 paper/paper.tex
Update conference name

\acmConference[GPCE '20]{Haskell '20: Proceedings of the 13th
  ACM SIGPLAN International Symposium on Haskell}{November 15 -- 20, 2020}{Chicago, Illinois, United States}
\acmBooktitle{Proceedings of the 19th ACM SIGPLAN International
Conference on Generative Programming: Concepts and Experiences (GPCE '20)
  November 15 -- 20, 2020, Chicago, Illinois, United States}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

>>>>

\acmConference[GPCE '20]{GPCE '20: Proceedings of the 13th
  ACM SIGPLAN International Symposium on Haskell}{November 15 -- 20, 2020}{Chicago, Illinois, United States}
\acmBooktitle{Proceedings of the 19th ACM SIGPLAN International
Conference on Generative Programming: Concepts and Experiences (GPCE '20)
  November 15 -- 20, 2020, Chicago, Illinois, United States}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}
